### 2025-05-04 Latex_Paper/Paper.tex
update all

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}

\usepackage[margin=1in]{geometry}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0em}
\makeatletter
\def\@maketitle{
  \newpage
  \null
  \vskip 2em
  \begin{center}
  \let \footnote \thanks
    {\LARGE \@title \par}
    \vskip 1.5em
    {\large \lineskip .5em
      \begin{tabular}[t]{c}
        \@author
      \end{tabular}\par}
    \vskip 1em
    {\large \@date}
  \end{center}
  \par
  \vskip 1.5em}
\makeatother

\begin{document}

\title{Image Caption Generation With CLIP+GPT-2 Model}
\author{Siyuan Jing and Haonan Wu\\ Boston University \\ siyuan16@bu.edu and whn17@bu.edu}
\date{May 3, 2025}
\maketitle

\begin{abstract}
To be finished
\end{abstract}

\section{Introduction}
Image caption generation, the task of recognizing images to generate natural language descriptions, lies at the critical intersection of 
computer vision and natural language processing. 
It plays an important role in a variety of applications, including image retrieval, accessibility for the visually impaired, and automated image content processing.

Recent advances in vision-language models have enabled more accurate and 
fluent caption generation by leveraging large-scale pretraining on aligned image-text pairs 
. These models demonstrate remarkable capabilities in understanding visual content and 
translating it into coherent text descriptions.

Motivated by these developments, and after reviewing related 
literature \cite{Nukrai2022},we aim to replicate a CLIP+GPT-2 based 
image captioning system. Through this project, we seek to explore and deepen our understanding of 
machine learning, as well as its broader applications in fields such as computer vision and natural language generation.
\begin{itemize}
    \item Leverage the pretrained CLIP model to extract semantically rich image embeddings without the need for training a custom vision encoder.
    \item Utilize the generative capabilities of GPT-2 to produce fluent and coherent natural language captions.
    \item Bridge the gap between visual and textual modalities by introducing a projection layer that maps image embeddings into GPT-2's input space.
    \item Enable flexible and data-efficient image captioning, where the visual semantics guide the generation through prefix-based conditioning.
    \item Evaluate the quality of the generated captions using standard metrics such as BLEU and CIDEr, in order to quantitatively assess the model's accuracy and relevance.
\end{itemize}
\pagebreak
\section{Background and Related Work}

\subsection{CLIP(Contrastive Language-Image Pretraining)}
CLIP from OpenAI is a visual-language model. Instead of relying on 
task-specific supervised learning, CLIP is trained on a dataset of 400
 million image-text pairs collected from the internet using a contrastive 
 loss function. CLIP consists of two separate encoders: a visual encoder 
 (ResNet) for images, and a text encoder (Transformer) for captions. 
 Its ability to generate rich, semantically meaningful image 
 embeddings makes CLIP a powerful foundation for our systems and 
 an ideal visual component in our CLIP+GPT-2 image captioning pipeline. 
 For example, according to Mokady et al.\cite{Mokady2021}, it mentioned that the visual encoding capability of 
 CLIP can be used to embed and project the generated images into the input 
 space of GPT-2 to generate prefixes, which helps the final caption generation of GPT-2. Inspired by this article, we decided to study the CLIP architecture and implement related deployments.

 \subsection{CLIP(Contrastive Language-Image Pretraining)}
 GPT-2 is a large-scale language model based on the Transformer 
 decoder architecture proposed by Radford et al. \cite{Radford}. 
 According to the paper, Transformer completely replaces the traditional RNN or 
 CNN structure with self-attention, which is more efficient and accurate when processing 
 long sequence dependencies. Therefore, we consider implementing the transformer 
 structure as our decoder of the whole pipeline. Unlike the traditional 
 Transformer, which contains both encoder and decoder components, 
 GPT-2 uses only a decoder. This design enables the model to predict the next token based solely on previously generated tokens, 
 making the generated text semantically relevant and well suited for text generation tasks such as image captioning.

\begin{equation}
L = -\sum_{i \in I} \log \frac{\exp(\text{sim}(z_i, z_j)/\tau)}{\sum_{k \neq i}\exp(\text{sim}(z_i, z_k)/\tau)}
\end{equation}
where $\text{sim}(z_i, z_j)$ is the cosine similarity between embeddings, and $\tau$ is the temperature hyperparameter.

\subsection{Comparison to Classical Methods}
Prior to contrastive learning, traditional unsupervised feature learning methods included:
\begin{itemize}
  \item \textbf{Principal Component Analysis (PCA):} Projects data onto lower-dimensional eigenvectors
with maximal variance.
  \item \textbf{Autoencoders:} Learn representations by reconstructing input data through an encoder-decoder
framework.
\end{itemize}
We compare these classical approaches with SimCLR to understand its advantages and limitations.

\section{Methodology}

\subsection{Implementation Details}
\textbf{Backbone Network:} We use a ResNet-18 as the feature encoder. The final representation is fed into
a two-layer MLP projection head.

\textbf{Augmentation Pipeline:} SimCLR relies heavily on augmentations, which include:
\begin{itemize}
  \item Random crop and resize
  \item Color jittering
  \item Gaussian blur
  \item Horizontal flipping
\end{itemize}

\textbf{Training Details:} We train SimCLR on CIFAR-10 and STL-10 using:
\begin{itemize}
  \item Batch size: \{128, 256, 512\}
  \item Temperature parameter: \{0.07, 0.1, 0.5\}
  \item Optimizer: Adam with a learning rate of $3 \times 10^{-4}$
  \item Number of epochs: 200
\end{itemize}

\subsection{Evaluation Protocol}
We evaluate the quality of learned representations by training a simple linear classifier on top of the
frozen embeddings.

\section{Experiments and Results}

\subsection{Dataset and Preprocessing}
We conduct experiments on:
\begin{itemize}
  \item \textbf{CIFAR-10:} A 10-class dataset with 60,000 images.
  \item \textbf{STL-10:} A larger dataset often used for unsupervised learning benchmarks.
\end{itemize}

\subsection{Baseline Comparisons}
We compare SimCLR embeddings with:
\begin{itemize}
  \item PCA-based dimensionality reduction ($d = 128$)
  \item Autoencoders trained on the same dataset
  \item Supervised ResNet-18 trained on CIFAR-10
\end{itemize}

\begin{table}[h]
\centering
\begin{tabular}{lcc}
\toprule
Method & CIFAR-10 Accuracy (\%) & STL-10 Accuracy (\%) \\
\midrule
Supervised ResNet-18 & 92.5 & 85.4 \\
PCA + kNN & 45.6 & 38.2 \\
Autoencoder + kNN & 55.3 & 49.6 \\
SimCLR (Ours) & 80.2 & 76.4 \\
\bottomrule
\end{tabular}
\caption{Comparison of representation learning methods. SimCLR significantly outperforms classical techniques.}
\end{table}

\subsection{Ablation Studies}
\textbf{Effect of Temperature $\tau$:} We analyze how different values of $\tau$ in the contrastive loss impact performance.

\section{Discussion}

\subsection{Key Findings}
\begin{itemize}
  \item SimCLR significantly outperforms PCA and autoencoders in feature learning.
  \item The choice of augmentations greatly affects performance.
  \item Higher temperature values in contrastive loss lead to better separation of features.
\end{itemize}

\subsection{Future Work}
\begin{itemize}
  \item Extend to other self-supervised methods (e.g., BYOL, MoCo).
  \item Apply to domain adaptation tasks.
  \item Explore contrastive learning for text or multimodal applications.
\end{itemize}

\section{Conclusion}
Our empirical study demonstrates the effectiveness of contrastive learning via SimCLR for representation
learning. By systematically evaluating augmentation pipelines, batch sizes, and loss functions, we provide
insights into optimizing contrastive learning for different datasets.
\pagebreak
\begin{thebibliography}{99}
    \bibitem{Nukrai2022}
    Nukrai, D., Mokady, R., \& Globerson, A. (2022). Text-Only Training for Image Captioning using Noise-Injected CLIP. https://doi.org/10.48448/n7sq-p557

    \bibitem{Mokady2021}
    Mokady, R., Hertz, A., \& Bermano, A. H. (2021). ClipCap: CLIP Prefix for Image Captioning. http://arxiv.org/abs/2111.09734

    \bibitem{Radford}
    Radford, A., Wu, J., Child, R., Luan, D., Amodei, D., \& Sutskever, I. (2019). ``Language Models are Unsupervised Multitask Learners.'' OpenAI Technical Report.

    \bibitem{li2020oscar}
    Li, X., Yin, X., Li, C., Zhang, P., Hu, X., Zhang, L., Wang, L., Hu, H., Dong, L., Wei, F., Choi, Y., \& Gao, J. (2020). ``Oscar: Object-Semantics Aligned Pre-training for Vision-Language Tasks.'' ECCV 2020.

    \bibitem{mokady2021clipcap}
    Mokady, R., Hertz, A., \& Bermano, A. H. (2021). ``ClipCap: CLIP Prefix for Image Captioning.'' arXiv preprint arXiv:2111.09734.

    \bibitem{papineni2002bleu}
    Papineni, K., Roukos, S., Ward, T., \& Zhu, W. J. (2002). ``BLEU: a method for automatic evaluation of machine translation.'' ACL 2002.

    \bibitem{vedantam2015cider}
    Vedantam, R., Lawrence Zitnick, C., \& Parikh, D. (2015). ``CIDEr: Consensus-based image description evaluation.'' CVPR 2015.

    \bibitem{chen2020simple}
    Ting Chen, Simon Kornblith, Mohammad Norouzi, Geoffrey Hinton. ``A Simple Framework for Contrastive Learning of Visual Representations.'' ICML 2020.

    \bibitem{hinton2006reducing}
    Geoffrey Hinton, Ruslan Salakhutdinov. ``Reducing the Dimensionality of Data with Neural Networks.'' Science, 2006.
    \end{thebibliography}

\end{document}

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 
-Motivated by these developments, and after reviewing related 
-literature \cite{Nukrai2022},we aim to replicate a CLIP+GPT-2 based 
-image captioning system. Through this project, we seek to explore and deepen our understanding of 
+Motivated by this progress, we focus our project on replicating a CLIP+GPT-2-based image captioning system, with inspriation from Nukrai et al.\cite{Nukrai2022}.
+Through this project, we seek to explore and deepen our understanding of
 machine learning, as well as its broader applications in fields such as computer vision and natural language generation.
@@
 
-\subsection{CLIP(Contrastive Language-Image Pretraining)}
+    \subsection{Contrastive Language-Image Pretraining(CLIP)}
     CLIP from OpenAI is a visual-language model. Instead of relying on 
@@
 
- \subsection{CLIP(Contrastive Language-Image Pretraining)}
+    \subsection{Generative Pre-trained Transformer 2 (GPT-2)}
     GPT-2 is a large-scale language model based on the Transformer 
- decoder architecture proposed by Radford et al. \cite{Radford}. 
+    decoder architecture proposed by Radford et al.\cite{Radford}. 
     According to the paper, Transformer completely replaces the traditional RNN or 
@@
 
-\begin{equation}
-L = -\sum_{i \in I} \log \frac{\exp(\text{sim}(z_i, z_j)/\tau)}{\sum_{k \neq i}\exp(\text{sim}(z_i, z_k)/\tau)}
-\end{equation}
-where $\text{sim}(z_i, z_j)$ is the cosine similarity between embeddings, and $\tau$ is the temperature hyperparameter.
+    \subsection{Multi-Head Attention Mechanism}
+    Inspired by the \textit{``Attention Is All You Need''} paper 
+    \cite{vaswani2017attention}, we employ a multi-head attention 
+    mechanism as a cross-modal connector between the CLIP image embedding
+    and the GPT-2 language model. Instead of using a linear layer to directly 
+    project the CLIP features into the GPT-2 embedding space, we employ an 
+    attention mechanism that enables the model to selectively focus on 
+    different aspects of the visual features when generating each token 
+    in the caption, making the generated tokens more consistent with the 
+    image information. Multi-head Attention network allows the model to 
+    learn how different regions in the image affect language production.
 
-\subsection{Comparison to Classical Methods}
-Prior to contrastive learning, traditional unsupervised feature learning methods included:
-\begin{itemize}
-  \item \textbf{Principal Component Analysis (PCA):} Projects data onto lower-dimensional eigenvectors
-with maximal variance.
-  \item \textbf{Autoencoders:} Learn representations by reconstructing input data through an encoder-decoder
-framework.
-\end{itemize}
 We compare these classical approaches with SimCLR to understand its advantages and limitations.
-
+\pagebreak
 \section{Methodology}
@@
 \end{itemize}
+\begin{equation}
+    L = -\sum_{i \in I} \log \frac{\exp(\text{sim}(z_i, z_j)/\tau)}{\sum_{k \neq i}\exp(\text{sim}(z_i, z_k)/\tau)}
+    \end{equation}
+    where $\text{sim}(z_i, z_j)$ is the cosine similarity between embeddings, and $\tau$ is the temperature hyperparameter.
 
@@
 
-    \bibitem{li2020oscar}
-    Li, X., Yin, X., Li, C., Zhang, P., Hu, X., Zhang, L., Wang, L., Hu, H., Dong, L., Wei, F., Choi, Y., \& Gao, J.
-(2020).
-``Oscar: Object-Semantics Aligned Pre-training for Vision-Language Tasks.'' ECCV 2020.
+    \bibitem{vaswani2017attention}
+    Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., Kaiser, Ł., \& Polosukhin, I. (2017). ``Attention is all you need.'' 
+    Advances in Neural Information Processing Systems, 30.
 

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 machine learning, as well as its broader applications in fields such as computer vision and natural language generation.
+
+Our goal is to:
 \begin{itemize}
@@
 
-We compare these classical approaches with SimCLR to understand its advantages and limitations.
+We compare these advanced approaches of image caption generation to understand its 
+advantages and limitations, and implement these methods in the process of model training to get our own model.
 \pagebreak
@@
 \subsection{Implementation Details}
-\textbf{Backbone Network:} We use a ResNet-18 as the feature encoder. The final representation is fed into
-a two-layer MLP projection head.
+\textbf{Detail of Implementation and pipeline:} This is the pipeline of 
+our entire training process, which mainly includes multiple steps: 
+image input, feature extraction and encoding, feature processing, 
+feature decoding, model training and error evaluation. We will also 
+introduce the optimization we used.
 
@@
 
-\textbf{Training Details:} We train SimCLR on CIFAR-10 and STL-10 using:
+\textbf{Training Details:} We train our model using these hyperparameter after cross-validation:
 \begin{itemize}
-  \item Batch size: \{128, 256, 512\}
-  \item Temperature parameter: \{0.07, 0.1, 0.5\}
-  \item Optimizer: Adam with a learning rate of $3 \times 10^{-4}$
-  \item Number of epochs: 200
+  \item Prefix length: 40
+  \item Transformer layers: 8
+  \item Optimizer: Adam with a learning rate of $5 \times 10^{-5}$
+  \item Number of epochs: 20
+  \item Noise rate: 10\%
 \end{itemize}

### 2025-05-04 02_Train_Plus.py

@@ -352,7 +352,7 @@ def main():
                        help='Saves the model every i epochs')
     parser.add_argument('--save_steps', type=int, default=10000,
                        help='save_steps')
-    parser.add_argument('--bs', type=int, default=40,
+    parser.add_argument('--bs', type=int, default=64,
                        help='Batch size')
     parser.add_argument('--seed', type=int, default=42,
                        help='random seed')

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 \usepackage{microtype}
+% \usepackage{titlesec}
+% \titleformat{\subsubsection}[runin]
+%   {\normalfont\normalsize} 
+%   {\thesubsubsection}      
+%   {1em}                    
+%   {}                     
+%   []       
+% \titlespacing*{\subsubsection}
+%   {0pt}                       
+%   {1.5ex plus 0.5ex minus 0.2ex} 
+%   {0.8ex plus 0.2ex}                 
+\usepackage{tikz}
 
+\usetikzlibrary{shapes.geometric, arrows, positioning, fit, backgrounds}
+\setcounter{secnumdepth}{3}
+\setcounter{tocdepth}{3}
 \usepackage[margin=1in]{geometry}
@@
 
-\textbf{Augmentation Pipeline:} SimCLR relies heavily on augmentations, which include:
-\begin{itemize}
-  \item Random crop and resize
-  \item Color jittering
-  \item Gaussian blur
-  \item Horizontal flipping
-\end{itemize}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figure1.png}
+    \caption{CLIP+GPT-2 Training Pipeline}
+    \label{fig:architecture}
+    \end{figure}
+
+\subsubsection{Data Set}
+
+We utilize the MS COCO dataset \cite{COCO}for training and evaluation, 
+MS COCO (Microsoft Common Objects in Context) 
+is a large-scale image recognition, segmentation, 
+and annotation dataset that is widely used in research 
+in the field of computer vision, especially in tasks 
+such as image captioning, object detection, and semantic 
+segmentation. It contains 330K images with 5 captions each. 
+We will split our dataset into three parts: 80\% training, 10\% validation, 10\% testing.
+
+\subsubsection{ Data Preparation}
 \begin{equation}
@@
 
-    \bibitem{mokady2021clipcap}
-    Mokady, R., Hertz, A., \& Bermano, A. H. (2021). ``ClipCap: CLIP Prefix for Image Captioning.'' arXiv preprint arXiv:2111.09734.
+    \bibitem{COCO}
+    Xinlei Chen, Hao Fang, Tsung-Yi Lin, Ramakrishna Vedantam, Saurabh Gupta, Piotr Dollár, and C Lawrence Zitnick.
+2015.
+Microsoft coco captions: Data collection and evaluation server.
+arXiv preprint arXiv:1504.00325.
 

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 
-\subsubsection{ Data Preparation}
+    \subsubsection{Data Preparation}
+    After we get the original CLIP embedding, we will normalize it for better training performance. In the actual training process, 
+    we found that the trained model may be overly sensitive to some features of some pictures, 
+    so we add some noise to 10\% of the feature information of each picture to improve generalization ability and reduce overfitting. 
+    These embeddings can then be projected into the GPT-2 space for training.
+\pagebreak
+    \subsubsection{Model training}
+    Next, we use a multi-layer Transformer to map the 
+    CLIP embedding to the word embedding space of GPT-2 
+    to create a prefix. This prefix is then concatenated 
+    with the tokenized caption, which is generated in the data preparation stage,  
+    to form the whole input sequence for GPT-2. After receiving these input sequences, 
+    the GPT-2 model is trained for a set rounds of training loop to generate the caption of the corresponding image based on the given prefix and token.
+
+    \subsubsection{Optimization method}
+    For the weight matrix obtained after each round of training, we use sub-gradient descent 
+    to adjust the weights. Additionally, during the entire training process, we use cross-validation to 
+    find the optimal solution for multiple hyperparameters in the model, and reasonably control the learning rate to obtain better training results.
+\subsection{Loss and objective function for training process}
+
+We use the cross-entropy loss function to measure the difference between the caption generated by the model and the ground-truth captions. The loss function is defined as:
+
+\textbf{The Cross-entropy Loss Function:}
 \begin{equation}
-    L = -\sum_{i \in I} \log \frac{\exp(\text{sim}(z_i, z_j)/\tau)}{\sum_{k \neq i}\exp(\text{sim}(z_i, z_k)/\tau)}
+\text{Loss} = -\sum_{t=1}^{T} \log P_{\text{GPT-2}}(w_t \mid w_{<t}, \text{prefix})
 \end{equation}
-    where $\text{sim}(z_i, z_j)$ is the cosine similarity between embeddings, and $\tau$ is the temperature hyperparameter.
+
+Where:  
+\begin{itemize}
+    \item $T$ — the total number of tokens (words) in the caption  
+    \item $w_t$ — the actual word at position $t$ in the ground-truth caption  
+    \item $w_{<t}$ — the sequence of all previous words before time step $t$  
+    \item $\text{prefix}$ — the mapped image feature vector used to condition the generation  
+    \item $P_{\text{GPT-2}}(w_t \mid w_{<t}, \text{prefix})$ — the probability assigned by GPT-2 to word $w_t$ given previous words and the image prefix
+\end{itemize}
+
+This loss encourages the model to assign a higher 
+probability to the correct next word at each time step. 
+Minimizing the cross-entropy loss over the training data 
+helps the model generate captions that are more fluent 
+and accurate.
+
+\pagebreak
+\textbf{The Objective Function in Maximum Likelihood Estimation:}
+
+\begin{equation}
+\hat{\theta} = \arg\min_{\theta} -\sum_{i=1}^{N} \sum_{t=1}^{T_i} \log P_\theta(w_t^{(i)} \mid w_{<t}^{(i)}, \text{prefix}^{(i)})
+\end{equation}
+
+Where:
+\begin{itemize}
+    \item $\theta$ — model parameters, including GPT-2 weights and the parameters of the prefix mapping network  
+    \item $N$ — the total number of training samples (image-caption pairs)  
+    \item $T_i$ — the number of tokens in the $i$-th caption  
+    \item $w_t^{(i)}$ — the $t$-th word in the $i$-th ground-truth caption  
+    \item $w_{<t}^{(i)}$ — all previous words before position $t$ in the $i$-th caption  
+    \item $\text{prefix}^{(i)}$ — the mapped image features for the $i$-th image
+\end{itemize}
+
+This objective function aims to find the parameter set $\hat{\theta}$ that minimizes the total negative log-likelihood 
+across the training dataset. During training, the model updates $\theta$ using optimization 
+techniques such as gradient descent, guided by cross-validation to avoid overfitting and improve generalization.
 

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 \documentclass[11pt]{article}
+\usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage[utf8]{inputenc}
@@
 
-    \subsubsection{Data Set}
+    \subsubsection{DataSet}
 
@@
 techniques such as gradient descent, guided by cross-validation to avoid overfitting and improve generalization.
-
-\textbf{Training Details:} We train our model using these hyperparameter after cross-validation:
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{f2.png}
+    \caption{Training and validation loss over epochs}
+    \end{figure}
+\pagebreak
+\section{Experiments and Results}
+\subsection{Training Details}
+We train our model using these hyperparameter after cross-validation:
 \begin{itemize}
@@
   \item Transformer layers: 8
+  \item Number of epochs: 12
+  \item Noise rate: 10\%
   \item Optimizer: Adam with a learning rate of $5 \times 10^{-5}$
-  \item Number of epochs: 20
-  \item Noise rate: 10\%
 \end{itemize}
 
-\subsection{Evaluation Protocol}
-We evaluate the quality of learned representations by training a simple linear classifier on top of the
-frozen embeddings.
-
-\section{Experiments and Results}
-
-\subsection{Dataset and Preprocessing}
 We conduct experiments on:
 \begin{itemize}
-  \item \textbf{CIFAR-10:} A 10-class dataset with 60,000 images.
-  \item \textbf{STL-10:} A larger dataset often used for unsupervised learning benchmarks.
+  \item \textbf{COCO Image Dataset:}
+
+  Training set: 80, 000 images with 5 captions per image.
+
+  Validation set: 2,000 images.
+
 \end{itemize}
 
-\subsection{Baseline Comparisons}
-We compare SimCLR embeddings with:
+\subsection{Evaluation Metrics}
+After completing model training, we need to evaluate the quality of generated captions to assess the effectiveness of our approach. Therefore, we adopt two widely used 
+automatic evaluation metrics in the field of image captioning: BLEU and CIDEr.
 \begin{itemize}
-  \item PCA-based dimensionality reduction ($d = 128$)
-  \item Autoencoders trained on the same dataset
-  \item Supervised ResNet-18 trained on CIFAR-10
+    \item \textbf{Bilingual Evaluation Understudy }
+
+    BLEU is a baseline evaluation 
+    metric of our model that measures the accuracy of n-gram overlap between predicted captions 
+    and one or more real captions\cite{Papineni}. It emphasizes syntactic similarity and is particularly sensitive to exact word 
+    matching and word order. However, this criterion lacks semantic awareness and often penalizes correct words due to different word position information.
+
+    \item \textbf{Consensus-based Image Description Evaluation}
+    To address the shortcomings of the above evaluation method, we also chose the CIDEr
+     (Consensus-based Image Description Evaluation) \cite{vedantam2015cider}
+     evaluation metric, which is designed specifically for image 
+     captioning. It uses a TF-IDF weighted n-gram model to evaluate how well the 
+     generated captions match the manually generated captions. This design increases the 
+     weights of rare but informative words (e.g., nouns, verbs, adjectives, etc., which often contain unique image information) 
+     while reducing the weights of function words such as articles (a, the), quantifiers (some, many), and prepositions (in, on, at).
 \end{itemize}
 
-\begin{table}[h]
+\pagebreak
+\subsection{Generation Results}
+\textbf{Prediction Scores:}
+
+We compute BLEU and CIDEr on our test set and compare the original captions' scores with our outputs:
+\begin{figure}[h]
     \centering
-\begin{tabular}{lcc}
-\toprule
-Method & CIFAR-10 Accuracy (\%) & STL-10 Accuracy (\%) \\
-\midrule
-Supervised ResNet-18 & 92.5 & 85.4 \\
-PCA + kNN & 45.6 & 38.2 \\
-Autoencoder + kNN & 55.3 & 49.6 \\
-SimCLR (Ours) & 80.2 & 76.4 \\
-\bottomrule
-\end{tabular}
-\caption{Comparison of representation learning methods. SimCLR significantly outperforms classical techniques.}
-\end{table}
+    \includegraphics[width=0.8\textwidth]{f3.png}
+    \caption{Model vs Human Performance on Image Captioning}
+    \end{figure}
+\begin{itemize}
+    \item Human captions show better performance on longer word sequences, indicating more natural grammatical structure.
+    \item The CIDEr score shows our model can achieve 94.4\% of human-level consensus quality.
+\end{itemize}
+\pagebreak
+\textbf{Web-based Deployment for Real-time Captioning}
 
-\subsection{Ablation Studies}
-\textbf{Effect of Temperature $\tau$:} We analyze how different values of $\tau$ in the contrastive loss impact performance.
+We design and deploy a website to realize our model
+function. The website is able to upload images and load the pre-trained model to generate 
+captions within 10 seconds.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{F4.png}
+        \caption{Example 1}
+        \label{fig:upload}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.43\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{F5.png}
+        \caption{Example 2}
+        \label{fig:caption}
+    \end{subfigure}
+    \caption{Web demo of our deployed model: From image upload to automatic caption generation}
+    \label{fig:web_demo}
+\end{figure}
 
@@
 \begin{itemize}
-  \item SimCLR significantly outperforms PCA and autoencoders in feature learning.
-  \item The choice of augmentations greatly affects performance.
-  \item Higher temperature values in contrastive loss lead to better separation of features.
+  \item Automated organization of visual content:
+
+  Our model efficiently manages unlabeled images, reducing the need for manual effort.  
+  \item Effective CLIP-to-GPT-2 Mapping:
+
+  Our multi-head attention mechanism bridges visual and textual modalities for high-quality captions.
+  \item Noise Injection Boosts Generalization:
+
+  Introducing noise during training boosts generalization and helps create diverse, accurate captions.
 \end{itemize}
@@
 
-    \bibitem{papineni2002bleu}
+    \bibitem{Papineni}
     Papineni, K., Roukos, S., Ward, T., \& Zhu, W. J. (2002). ``BLEU: a method for automatic evaluation of machine translation.'' ACL 2002.
@@
 
-    \bibitem{chen2020simple}
-    Ting Chen, Simon Kornblith, Mohammad Norouzi, Geoffrey Hinton. ``A Simple Framework for Contrastive Learning of Visual Representations.'' ICML 2020.
-
-    \bibitem{hinton2006reducing}
-    Geoffrey Hinton, Ruslan Salakhutdinov. ``Reducing the Dimensionality of Data with Neural Networks.'' Science, 2006.
     \end{thebibliography}

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 \begin{itemize}
-  \item Extend to other self-supervised methods (e.g., BYOL, MoCo).
-  \item Apply to domain adaptation tasks.
-  \item Explore contrastive learning for text or multimodal applications.
+  \item 
+  \item 
+  \item 
 \end{itemize}
@@
 \section{Conclusion}
-Our empirical study demonstrates the effectiveness of contrastive learning via SimCLR for representation
-learning. By systematically evaluating augmentation pipelines, batch sizes, and loss functions, we provide
-insights into optimizing contrastive learning for different datasets.
+
 \pagebreak

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 
-  Our model efficiently manages unlabeled images, reducing the need for manual effort.  
+    Our model demonstrates strong automatic organization 
+    capabilities for visual content, especially when dealing 
+    with a large number of unlabeled images. By generating 
+    relevant and informative captions, the system can group 
+    images without manual annotation.
+
         \item Effective CLIP-to-GPT-2 Mapping:
 
-  Our multi-head attention mechanism bridges visual and textual modalities for high-quality captions.
+    The key design of our entire model is the multi-head 
+    attention mechanism used to connect CLIP visual embedding
+    and GPT-2 language model input. Unlike simple linear projection, 
+    the multi-head attention mechanism enables the model to learn 
+    multiple semantic alignment patterns between image features and 
+    different dimensions of generated captions. Test results show 
+    that the implementation of this mechanism can generate more 
+    accurate captions that reflect the details of image semantics.
+
     \item Noise Injection Boosts Generalization:
+    We observe that adding small Gaussian noise into CLIP embeddings 
+    during training improves the model's generalization across 
+    different image inputs. This regularization technique helps 
+    the mapping module avoid overfitting to specific embedding 
+    patterns and encourages the model to generate captions that
+    are both accurate and diverse. Result shows that noise
+    improves both BLEU and CIDEr scores, indicating improved
+    robustness and semantic coverage of caption generation.
 
-  Introducing noise during training boosts generalization and helps create diverse, accurate captions.
 \end{itemize}
@@
 \subsection{Future Work}
-\begin{itemize}
-  \item 
-  \item 
-  \item 
-\end{itemize}
+In future work, we plan to expand the test 
+dataset to cover more diverse and challenging images to 
+more robustly evaluate the generalization ability of our model. 
+In addition, we can try to study and combine more powerful visual 
+language models (such as CLIP ViT-L or GPT-3 variants) to achieve 
+stronger semantic alignment capabilities.
 
 \section{Conclusion}
+In this project, we implemented an image captioning 
+system by combining the powerful visual encoding capabilities 
+of CLIP and the generative language capabilities of GPT-2. By 
+introducing a mapping module based on a multi-head attention 
+mechanism, we effectively reduced the gap between visual and 
+textual modalities, enabling the generation of fluent and 
+semantically relevant captions. We further enhanced the 
+generalization ability of the model by adding noise during training, and selected appropriate loss functions and objective functions for training.
+Finally, evaluations using BLEU and CIDEr metrics confirmed the effectiveness of our model, especially in capturing human-written semantics, with the CIDEr score reflecting its excellent performance.
 

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
 \begin{abstract}
-To be finished
+        This paper presents an image captioning system that combines CLIP with GPT-2.
+        We implement a multi-head attention mechanism to effectively bridge the gap between visual and textual modalities. 
+        Trained on the MS COCO dataset, 
+        our model achieves 94.4\% of human-level consensus quality as 
+        measured by CIDEr scores. Our experiments show that the proposed architecture effectively 
+        captures both semantic  and syntactic structure in generating natural language descriptions. Additionally, 
+        we develop a web-based deployment for real-time captioning that processes images within 10 seconds.
+        The results highlight the potential of leveraging pre-trained vision and language 
+        models for efficient multimodal understanding with minimal architectural modifications. Codes are avalibale at \url{https://github.com/ChingSsuyuan/Clip_Pro_Caption.git}
 \end{abstract}

### 2025-05-04 Latex_Paper/Paper.tex
update all

@@
         This paper presents an image captioning system that combines CLIP with GPT-2.
-        We implement a multi-head attention mechanism to effectively bridge the gap between visual and textual modalities. 
+        We implement a multi-head attention mechanism to effectively bridge between visual and textual modalities. 
         Trained on the MS COCO dataset, 
@@
         captures both semantic  and syntactic structure in generating natural language descriptions. Additionally, 
-        we develop a web-based deployment for real-time captioning that processes images within 10 seconds.
+        we develop a web-based deployment for real-time captioning
         The results highlight the potential of leveraging pre-trained vision and language 
@@
 \end{itemize}
-\pagebreak
+
 \section{Background and Related Work}
